A comparison of two second order traffic flow models

### 2015-03-13 FirstDraftMaterials/Draft.tex
Adding edits.

\begin{enumerate}[(a)]
\item Integral form of equation: $\displaystyle \frac{d}{dt} \int_{x_1}^{x_2} \rho \, dt = -\Big[ f( \rho ) \Big]_{x_1}^{x_2}$
\item Differential form of equation: $\rho_t + f( \rho )_x = \rho_t + \Big( \rho V(\rho) \Big)_x = 0$
\end{enumerate}

@@

\begin{enumerate}[(a)]
\item Integral form of equation: $\displaystyle \frac{d}{dt} \int_{x_1}^{x_2} \rho v \, dt = -\Big[ f( \rho v ) \Big]_{x_1}^{x_2}$
\item Differential form of equation: $(\rho v)_t + f( \rho v )_x = (\rho v)_t + \Big( \rho v^2 + p(\rho) \Big)_x = 0$
\end{enumerate}

@@

Restrictions on the way that $\lambda$ must vary across a wave allow us to identify the regions of the Hugoniot loci and integral curves that are valid for any given point. When traveling across a shock from a left state, $q_l$, to a right state $q_r$, $\lambda$ must decrease. When traveling across a rarefaction wave from a left state, $q_l$, to a right state $q_r$, $\lambda$ must increase. In Figure \ref{fig:PW_curves} (c) and (d) we see the Hugoniot loci and integral curves for this system with the contour lines for $\lambda_1$ and $\lambda_2$. Using these plots, we can determine which areas of the curves are valid shocks and which are valid rarefaction waves. Figure \ref{fig:PW_curves} (e) and (d) shows the points $q_l$ and $q_r$, respectively, with only the valid waves displayed. For these plots,
$q_* = (\rho_*,\rho_*v_*) = (0.2, 0.04)$ and $\gamma = 0.2$. 
Here, shocks are shown in red or magenta and rarefaction waves are shown in either light or dark green.

@@

Therefore, it is important to take into account the contour lines of $\lambda$ when 
looking at the loci and integral curves. Figure \ref{fig:AR_validity}(a) 
shows the $\lambda_1$-curves in the $M$ plane,
with the contour lines of $\lambda_1$ shown in magenta. This information is used
to determine which areas of the $\lambda_1$ curves are valid shock waves and which
are valid rarefaction waves. The rest of the subfigures show the regions of validity for 
specific points $q_*$, depending on whether $q_* = q_l$ or $q_* = q_r$. For these plots,
$q_* = (\rho_*,\rho_*v_*) = (0.2, 0.04)$ and $\gamma = 0.2$. Note that the contact discontinuity is valid
anywhere in the plane since $\lambda_2$ is linearly degenerate.

@@

In the second example, we consider the case where there are no cars on the left.  Once again the AR model predicts what we would expect.  Here the cars continue to move to the right at a constant velocity, while the state on the left remains zero.  Note that in Clawpack solutions the density and velocity are undefined in the middle, but that this is a result of numerical issues.  In reality they should both be zero.  The PW method again fails to produce reasonable results.  Not only does it predict negative velocities, but we can see from the density plot that some cars have in fact moved backwards into the left region.  While it would make sense for fluids to act this way, we do not expect drivers to start moving in reverse when they see that nobody is behind them!

>>>>

\begin{enumerate}[(a)]
\item Integral form of equation: $\displaystyle \frac{d}{dt} \int_{x_1}^{x_2} \rho \, dx = -\Big[ f( \rho ) \Big]_{x_1}^{x_2}$
\item Differential form of equation: $\rho_t + f( \rho )_x = \rho_t + \Big( \rho V(\rho) \Big)_x = 0$
\end{enumerate}

@@

\begin{enumerate}[(a)]
\item Integral form of equation: $\displaystyle \frac{d}{dt} \int_{x_1}^{x_2} \rho v \, dx = -\Big[ f( \rho v ) \Big]_{x_1}^{x_2}$
\item Differential form of equation: $(\rho v)_t + f( \rho v )_x = (\rho v)_t + \Big( \rho v^2 + p(\rho) \Big)_x = 0$
\end{enumerate}

@@

Restrictions on the way that $\lambda$ must vary across a wave allow us to identify the regions of the Hugoniot loci and integral curves that are valid for any given point. When traveling across a shock from a left state, $q_l$, to a right state $q_r$, $\lambda$ must decrease. When traveling across a rarefaction wave from a left state, $q_l$, to a right state $q_r$, $\lambda$ must increase. In Figure \ref{fig:PW_curves} (c) and (d) we see the Hugoniot loci and integral curves for this system with the contour lines for $\lambda_1$ and $\lambda_2$. Using these plots, we can determine which areas of the curves are valid shocks and which are valid rarefaction waves. Figure \ref{fig:PW_curves} (e) and (f) shows the points $q_l$ and $q_r$, respectively, with only the valid waves displayed. For these plots,
$q_* = (\rho_*,\rho_*v_*) = (0.2, 0.04)$ and $\gamma = 0.2$. 
Here, shocks are shown in red or magenta and rarefaction waves are shown in either light or dark green.

@@

Therefore, it is important to take into account the contour lines of $\lambda$ when 
looking at the loci and integral curves. Figure \ref{fig:AR_validity}(a) 
shows the $\lambda_1$-curves in the $M$ plane,
with the contour lines of $\lambda_1$ shown in cyan. This information is used
to determine which areas of the $\lambda_1$ curves are valid shock waves and which
are valid rarefaction waves. The rest of the subfigures show the regions of validity for 
specific points $q_*$, depending on whether $q_* = q_l$ or $q_* = q_r$. For these plots,
$q_* = (\rho_*,\rho_*v_*) = (0.2, 0.04)$ and $\gamma = 0.2$. Note that the contact discontinuity is valid
anywhere in the plane since $\lambda_2$ is linearly degenerate.

@@

In the second example, we consider the case where there are no cars on the left. In figure \ref{fig:example2}, note that there are two valid curves for both models. In order to determine which curve is the correct one to follow, we considered a case when we had a very small density in the left state (rather than a zero density) and then considered the limit as the density on the left went to zero. This analysis made it clear that for the AR model the correct curve to follow is the contact discontinuity between $q_l$ and $q_r$, and for the PW model the correct curve to follow is the integral curve between $q_l$ and $q_r$.

Once again the AR model predicts what we would expect.  Here the cars continue to move to the right at a constant velocity, while the state on the left remains zero. The PW method again fails to produce reasonable results.  Not only does it predict negative velocities, but we can see from the density plot that some cars have in fact moved backwards into the left region.  While it would make sense for fluids to act this way, we do not expect drivers to start moving in reverse when they see that nobody is behind them!
